---
title: 'Correspondence Analysis'
author: 'Dataset data'
output:
  html_document: default
---
This dataset contains 20 rows and 6 columns, 10 rows are considered as illustrative, 1 additional variable is qualitative and considered as illustrative.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('E:/Fifth_Sem/R Analysis/Workspace.RData')
```
### 1. Study of the outliers
The detection of outliers does not apply to CA results.

### 2. Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of analyse express **90.52%** of the total dataset inertia ; that means that 90.52% of the rows (or columns) cloud total variability is explained by the plane.
This percentage is very high and thus the first plane represents very well the data variability.
This value is greater than the reference value that equals **81.44%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 312 data tables of equivalent size on the basis of a uniform distribution).

From these observations, it is not necessary to interpret the next dimensions.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
ggplot2::ggplot(cbind.data.frame(x=1:nrow(res$eig),y=res$eig[,2])) + ggplot2::aes(x=x, y=y)+ ggplot2::geom_col(fill="blue") + ggplot2::xlab("Dimension") + ggplot2::ylab("Percentage of variance") + ggplot2::ggtitle("Decomposition of the total inertia") + ggplot2::theme_light() + ggplot2::theme(plot.title = ggplot2::element_text(hjust =0.5)) + ggplot2::scale_x_continuous(breaks=1:nrow(res$eig))
```

**Figure 2 - Decomposition of the total inertia**

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 2 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (90.52% against 81.44%).
This observation suggests that only these axis are carrying a real information.
As a consequence, the description will stand to these axis.

- - -

### 3. Description of the plane 1:2

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
r.drawn <-
c("2", "3", "8", "11", "1")
c.drawn <-
c("Cause", "F.C1", "M.C3", "F.C2", "M.C1", "F.C3")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.CA(res, selectRow = r.drawn, selectCol = c.drawn, axes = 1:2, choix = 'CA', invisible = c('var', 'quali'), title = '', cex = cex)
```

**Figure 3.1 - Overlayed factor map (CA)**
*The rows in light blue are considered as active whereas those in dark blue are illustrative.*
*The labeled rows are those with the higher contribution to the plane construction.*
*The labeled columns are those the best shown on the plane.*

